First steps towards a formalization of Forcing

### 2018-06-24 LSFA/intro.tex
dejo addressed
Lawrence is back

A great part of G\"odel's work on this subject has been formalized in
Isabelle by Larry Paulson. This paper formalizes a first part of the
machinery of forcing. In the rest of the introduction we discuss some
of the set-theoretical details involved and explain briefly Paulson's
formalization.

@@

%% MIGUEL: redacción alternativa del párrafo siguiente.
Every  $y \in M[G]$ is obtained from an element $\dot y$ of $M$, thus
elements of $M$ are construed as \emph{names} or codes for elements of
$M[G]$.
The decoding is given by the function
$\val$ which takes the generic filter $G$ as a parameter. To
prove that $M$ is contained in $M[G]$ it suffices to give a name for
each element of $M$; we define the function $\chk$ which assigns
a name for each $x\in M$. Showing that $\chk(x)\in M$
when $x\in M$ involves some technical issues that will
be addressed/formalized in a further work. We explain names, $\val$, and
$\chk$ in Section~\ref{sec:names}.

>>>>

A great part of G\"odel's work on this subject has been formalized in
Isabelle by Lawrence Paulson. This paper formalizes a first part of the
machinery of forcing. In the rest of the introduction we discuss some
of the set-theoretical details involved and explain briefly Paulson's
formalization.

@@

%% MIGUEL: redacción alternativa del párrafo siguiente.
Every  $y \in M[G]$ is obtained from an element $\dot y$ of $M$, thus
elements of $M$ are construed as \emph{names} or codes for elements of
$M[G]$.
The decoding is given by the function
$\val$ which takes the generic filter $G$ as a parameter. To
prove that $M$ is contained in $M[G]$ it suffices to give a name for
each element of $M$; we define the function $\chk$ which assigns
a name for each $x\in M$. Showing that $\chk(x)\in M$
when $x\in M$ involves some technical issues that will
be addressed in a further work. We explain names, $\val$, and
$\chk$ in Section~\ref{sec:names}.
